### 2019-01-03 tex/appendix.tex
Semantic segmentation experiments added. List of hyperparameters added.

{\proposition The objective function $\widetilde{E}({\bf z})$ of (T-LP-FULL) is the Lovasz extension of $F_{r-\textrm{HST}}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
%\label{proposition:rhst_optimal}}
\begin{proof}
    We observe that $F_{r-\textrm{HST}}$ is of exactly the same form as
    $F_{Potts}$, except that the Ising models $F_i$ are defined over not just labels, but meta-labels as well. Using the same logic as in the proof of Potts extension, each $F_i$ is the Lovasz extension of 
        \begin{equation}
            \widetilde{E}_i({\bf z}) = \left( \sum_{a \in {\mathcal X}} \phi_a'(i) \cdot z_{ai} + \sum_{(a, b) \in {\mathcal N}} w_{ab} \cdot l_{T_i} \cdot |z_{ai} - z_{bi}| \right)
        \end{equation}
    and the results follows. 
\end{proof}
\iffalse
\section{Additional Experiment Results}

>>>>

{\proposition The objective function $\widetilde{E}({\bf z})$ of (T-LP-FULL) is the Lovasz extension of $F_{r-\textrm{HST}}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
%\label{proposition:rhst_optimal}}
\begin{proof}
    We observe that $F_{r-\textrm{HST}}$ is of exactly the same form as
    $F_{Potts}$, except that the Ising models $F_i$ are defined over not just labels, but meta-labels as well. Using the same logic as in the proof of Potts extension, each $F_i$ is the Lovasz extension of 
        \begin{equation}
            \widetilde{E}_i({\bf z}) = \left( \sum_{a \in {\mathcal X}} \phi_a'(i) \cdot z_{ai} + \sum_{(a, b) \in {\mathcal N}} w_{ab} \cdot l_{T_i} \cdot |z_{ai} - z_{bi}| \right)
        \end{equation}
    and the results follows. 
\end{proof}

\mysection{List of Hyperparameters}

For pairwise dense CRFs, following \cite{koltun2011efficient}, we use constrast-sensitive two-kernel potentials for both stereo matching and semantic segmentation. These are defined in terms of the color vectors ${I}_a$ and ${I}_b$ and positions $p_a$ and $p_b$ as:

\begin{equation}
k({\bf f}_a, {\bf f}_b) = w^{(1)}\exp\left(- \frac{|p_a - p_b|^2}{2 \theta_{\alpha}^2} - \frac{|{I}_a - {I}_b|^2}{2 \theta_{\beta}^2}\right) + w^{(2)}\exp\left(- \frac{|p_a - p_b|^2}{2 \theta_{\gamma}^2}\right) 
\end{equation}

For the higher-order diversity model, we have a clique weight $w_c$ that is the same across all cliques. We give the set of hyperparameters for our experiments in table \ref{tab:hyper}.

\begin{table}[]
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
{} &  $w^{(1)}$ & $\theta_{\alpha}$ & $\theta_{\beta}$ &  $w^{(1)}$ & $\theta_{\gamma}$ & $w_c$\\
\hline
Stereo matching (dense pairwise, Submod) & 1.64 & 12.99 & 50.84 &  1.51 & 1.10 & 0  \\
\hline
Stereo matching (dense pairwise, MF) & 12.43 & 22.38 & 17.26 & 4.59 & 8.75 & 0  \\
\hline
Stereo matching (higher-order, Submod) & 12.43 & 22.38 & 17.26 & 4.59 & 8.75 & 10.00 \\
\hline
Semantic Segmentation (higher-order, Submod) & 1.00 & 1.00 & 50.84 & 1.51 & 1.10 & 10.00 \\
\hline
\end{tabular}
\caption{List of hyperparameters used in experiments}
\label{tab:hyper}
\end{table}

\iffalse
\section{Additional Experiment Results}

### 2019-01-03 tex/paper.tex
Semantic segmentation experiments added. List of hyperparameters added.

\begin{figure*}
    \centering
\begin{tabular}{ccc}
        \includegraphics[scale = 0.24]{\imagePath/stereo/venus_GT} &
        \includegraphics[scale = 0.24]{\imagePath/stereo/potts/venus_left_mf} &
        \includegraphics[scale = 0.24]{\imagePath/stereo/potts/venus_left_submod} \\
\end{tabular}
\mycaption{\footnotesize \em To fill}
%\label{fig:stereo}
\end{figure*}

@@

\myparagraph{Results} The ground-truth labelings provided with the MSRC-21
dataset are very coarse. We evaluate our algorithm on the set of 94 images for which fine-grain
annotations are available \citep{koltun2011efficient}. On this subset, our
method correctly labeled 81.18\% of pixels. Some representative results are
shown in figure \ref{}. Our set of hyperparameters for this dataset can be found in the
appendix.

>>>>

\begin{figure*}
    \centering
\begin{tabular}{cc}
  \includegraphics[scale = 1.3]{./figures/semantic/2_14_s} &
  \includegraphics[scale = 0.5]{./figures/semantic/2_14_s_submod} \\
        \scriptsize (a) & \scriptsize (e) \\
  \includegraphics[scale = 1.3]{./figures/semantic/11_4_s} &
  \includegraphics[scale = 0.5]{./figures/semantic/11_4_s_submod} \\
        \scriptsize (b) & \scriptsize (f) \\
  \includegraphics[scale = 1.3]{./figures/semantic/12_7_s} &
  \includegraphics[scale = 0.5]{./figures/semantic/12_7_s_submod} \\
        \scriptsize (c) & \scriptsize (g) \\
  \includegraphics[scale = 1.3]{./figures/semantic/4_16_s} &
  \includegraphics[scale = 0.5]{./figures/semantic/4_16_s_submod} \\
        \scriptsize (d) & \scriptsize (h) \\
\end{tabular}
\mycaption{\footnotesize \em Sample results from semantic segmentation on the
MSRC-21 dataset using dense CRFs with higher-order diversity term in addition
to Potts compatibility and Gaussian pairwise potentials. (a)-(d) show the input
image, and (e)-(f) show the corresponding results using our method. We observe that our
method is able to segment out objects with complex boundaries fairly
accurately.}
\label{fig:semantic}
\end{figure*}

@@

\myparagraph{Results} The ground-truth labelings provided with the MSRC-21
dataset are very coarse. We evaluate our algorithm on the set of 94 images for which fine-grain
annotations are available \citep{koltun2011efficient}. On this subset, our
method correctly labeled 81.18\% of pixels. It took 275.02s on average per
instance to run our method for 100 iterations. Some representative results are
shown in figure \ref{fig:semantic} where we label each pixel with the label
having the maximum marginal probability. Our set of hyperparameters for this dataset can be found in the
appendix.
